\documentclass{scrartcl}
\usepackage{mrk}

\title{This is a Title}


\begin{document}

\maketitle



\section{Standard Environments}

this is a test \rr[2m+3]. This is a test $\ad X$ blah \ff blah blah $\brac{x+y}$. blah $\mathrm{diag}$ $\proj X$ text blah text blah text blah text blah text blah

\[
\begin{tikzcd}
    A \arrow[r, "\phi"] \arrow[d, red]
    & B \arrow[d, "\psi" red] \\
    C \arrow[r, red, "\eta" blue]
    & D
    \end{tikzcd}\]


\begin{theorem}
    This is a theorem!
\end{theorem}
\begin{lemma}
    This is a lemma!
\end{lemma}
\begin{proposition}
    This is a proposition!
\end{proposition}
\begin{corollary}
    This is a corollary!
\end{corollary}
\begin{conjecture}
    This is a conjecture!
\end{conjecture}
\begin{problem}
    This is a problem!
\end{problem}
\begin{example}
    This is a example!
\end{example}
\begin{question}
    This is a question!
\end{question}
\begin{remark}
    This is a remark!
\end{remark}

\newpage

\section{Boxed Environments}
\begin{theorembox}
    This is a theorembox!
\end{theorembox}
\begin{lemmabox}
    This is a lemmabox!
\end{lemmabox}
\begin{propbox}
    This is a propbox!
\end{propbox}
\begin{corollarybox}
    This is a corollarybox!
\end{corollarybox}
\begin{conjecturebox}
    This is a conjecturebox!
\end{conjecturebox}
\begin{claimbox}
    This is a claimbox!
\end{claimbox}
\begin{problembox}
    This is a problembox!
\end{problembox}
\begin{examplebox}
    This is a examplebox!
\end{examplebox}
\begin{questionbox}
    This is a question!
\end{questionbox}
\begin{remarkbox}
    This is a remarkbox!
\end{remarkbox}

\newpage

\section{Proof Environments}
\begin{proof}
    Test proof!
\end{proof}
\begin{subproof}
    Test subproof!
\end{subproof}
\begin{proof*}{My Proof}
    Test proof*!
\end{proof*}
\begin{subproof*}{My Subproof}
    Test subproof*!
\end{subproof*}




\end{document}
